%-------------------------
% Resume in Latex
% Author : Abhishek Mane
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\Large Abhishek Mane}} \\[4pt]
  \small
  \href{mailto:abhishek.mane.work@gmail.com}{abhishek.mane.work@gmail.com} $|$
  +91-7020870063 $|$
  Ahmedabad, Gujarat, India \\[2pt]
  \href{https://www.linkedin.com/in/abhishek-mane-aiml}{linkedin.com/in/abhishek-mane-aiml} $|$
  \href{https://substack.com/@abhimane}{substack.com/@abhimane} $|$
  \href{https://github.com/abhishekmane6122}{github.com/abhishekmane6122}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Terna Engineering College}{Osmanabad, India}
      {Bachelor of Technology -- Artificial Intelligence and Data Science}{Dec. 2021 -- 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CognitBotz Solutions}{Ahmedabad, India}
      {Artificial Intelligence Engineer -- Client: Adani Green Energy \& Adani Group}{Sep. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Aegis -- Enterprise Compliance Platform}
          {Designed and developed a full-stack, production-grade compliance intelligence platform for Adani Group's Secretarial \& Legal teams. Built six independently deployable modules -- BSE Intelligence, RBI Compliance, SEBI Hub, Director Disclosure Management, Insider Trading Surveillance, and Minutes Preparation -- behind a unified React UI. Platform saved \textbf{250+ FTE hours per quarter} and is live in production.}
        \resumeItem{Regulatory RAG Pipeline (BSE, SEBI, RBI)}
          {Engineered automated scraping and ingestion pipelines (using Playwright and Requests) that collect daily notifications from BSE, SEBI, and RBI portals, extract content from PDFs via PyMuPDF and OCR, and generate AI summaries using Phi-3-mini LLM. Indexed documents into ChromaDB vector store for semantic search and pushed structured data to Azure PostgreSQL. Delivered automated daily email reports via SMTP. Eliminated \textbf{6+ hours of manual daily monitoring} and reduced SEBI notification noise by \textbf{71\%}.}
        \resumeItem{Multi-Agent NL-to-SQL System}
          {Designed a multi-agent architecture where a routing agent classifies user intent and delegates to either a deterministic query handler or a GPT-powered dynamic SQL generation agent. Engineered prompt templates with schema context injection for SAP HANA-compatible SQL generation. Built a query validation layer to sanitize LLM output, prevent SQL injection, and enforce read-only access.}
        \resumeItem{Equity Pulse -- Market Analytics Platform}
          {Built an end-to-end equity analytics platform for Adani Group's finance and portfolio teams. Designed ETL pipelines on a scheduled VM to extract, validate, and load daily bhavcopy data from BSE and NSE into Azure PostgreSQL. Developed a backend computation engine to calculate moving averages, volatility metrics, delivery ratios, and relative performance indices. Built the React frontend with interactive dashboards, candlestick charts, competitor analysis, and shareholding pattern tracking across \textbf{7 Adani business units} and \textbf{3.9M+ investor records}. Eliminated \textbf{4--6 hours of daily manual analyst work}.}
        \resumeItem{Platform Infrastructure \& Observability}
          {Implemented Azure AD SSO with RBAC across all platforms. Secured all secrets via Azure Key Vault, enforced TLS in transit and AES-256 encryption at rest. Built a custom \textbf{AI Agent Observability Platform} to monitor all deployed agents in real time -- covering health checks, execution logs, latency tracking, and failure alerts. Configured Azure VM scheduling for automated pipeline execution and optimized API response times from \textbf{8 seconds to 500ms}. Integrated email-based triggers and automated reporting via SMTP for daily operational summaries.}
        \resumeItem{Cross-Functional Technical Leadership}
          {Act as de facto technical lead across all enterprise AI projects at CognitBotz. Lead daily Scrum meetings with a \textbf{15+ member cross-functional team} spanning Data Engineers, Python Developers, AI/ML Engineers, and Frontend Developers. Directly engaged in stakeholder management with Adani Group leadership -- conducting project progress updates, requirements gathering sessions, and sprint reviews to ensure delivery alignment with business objectives.}
      \resumeItemListEnd

    \resumeSubheading
      {CognitBotz Solutions}{Hyderabad, India}
      {Artificial Intelligence Engineer}{Nov. 2024 -- Sep. 2025}
      \resumeItemListStart
        \resumeItem{LLM Engineering \& Deployment}
          {Developed and fine-tuned LLMs using LangChain and Agno with few-shot and transfer learning. Designed APIs for LLM integration and deployed production chatbots, Q\&A systems, and web agents handling text, documents, and multi-modal inputs.}
        \resumeItem{AI Evaluation \& Responsible AI}
          {Evaluated LLM performance on accuracy, relevance, and fairness metrics. Implemented bias mitigation, data privacy safeguards, and responsible AI practices to prevent misuse and harmful content generation.}
      \resumeItemListEnd

    \resumeSubheading
      {Infosys Springboard}{India}
      {Artificial Intelligence Developer (Internship)}{Sep. 2024 -- Dec. 2024}
      \resumeItemListStart
        \resumeItem{AI Application Development}
          {Built AI/ML applications under the Infosys Springboard program, gaining hands-on experience with enterprise AI workflows and NLP pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {Cyber Crime Police Station -- India}{Osmanabad, India}
      {Data Analyst}{Oct. 2023 -- Jan. 2024}
      \resumeItemListStart
        \resumeItem{Data Management}
          {Managed user credentials for the National Cyber Crime Reporting Portal. Extracted and organized complaint data in Excel to improve case handling efficiency. Maintained portal by updating complaint statuses and coordinating directly with victims on case resolutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Aegis -- Regulatory Compliance Intelligence Suite $|$ \textit{CognitBotz, Client: Adani Group}}
      {Production-grade multi-module platform automating BSE/SEBI/RBI monitoring, director disclosure management, insider trading surveillance across 3.9M+ investor records, and board meeting minutes generation. Saved \textbf{250+ FTE hours/quarter}. \textit{Stack: React, FastAPI, Python, LangChain, LangGraph, Azure OpenAI, Cohere Embeddings, pgvector (Azure PostgreSQL), Azure Key Vault, Azure VM, Nginx, Docker, GitLab.}}
    \resumeSubItem{Equity Pulse -- Enterprise Equity Analytics Platform $|$ \textit{CognitBotz, Client: Adani Group}}
      {End-to-end equity analytics platform tracking 5 Adani business units with automated ETL from BSE/NSE, real-time dashboards, candlestick charts, competitor analysis, and shareholding pattern portal across \textbf{3.9M+ investor records}. Eliminated 4--6 hrs of daily manual analyst work. \textit{Stack: React, TypeScript, FastAPI, Python, Azure PostgreSQL, pgvector, Azure VM, APScheduler, Recharts, Docker, GitLab.}}
    \resumeSubItem{Quantus Med -- Multimodal AI Clinical Diagnostic Intelligence $|$ \textit{CognitBotz}}
      {Clinical AI platform fusing medical imagery (DICOM/JPG/PNG) with real-time physician voice dictation to generate structured SOAP diagnostic reports in under \textbf{500ms}. Uses Llama-3 and Gemini 1.5-Flash for vision, Whisper-large-v3 for transcription, and Edge-TTS for hands-free playback. HIPAA/GDPR-compliant zero-knowledge inference. \textit{Stack: React-Vite, FastAPI, LangChain, Groq LPU, Llama-3, Gemini 1.5-Flash, Whisper-large-v3, Edge-TTS.}}
    \resumeSubItem{Doc Capture -- Intelligent Document Extraction API $|$ \textit{CognitBotz}}
      {FastAPI backend for automated extraction and export of structured data from multi-type documents (Aadhaar, PAN, Driving License, Voter ID, invoices). Supports template-based invoice mapping, batch processing, and Excel/JSON export. Docker Compose deployed. \textit{Stack: Python, FastAPI, Groq LLM, PyMuPDF, Camelot, Openpyxl, Docker.}}
    \resumeSubItem{OmniQA-Agent -- Autonomous Requirements \& Test Engineering Orchestrator $|$ \textit{Personal}}
      {Autonomous QA platform crawling websites via Playwright headless Chromium, parsing DOM with BeautifulSoup, and orchestrating LangChain pipelines through Groq Llama-4 to auto-generate user stories, test plans, and test cases. Exports color-formatted Excel workbooks ready for Jira/ALM integration. \textit{Stack: Python, Streamlit, Playwright, BeautifulSoup4, LangChain, Groq (Llama-4), Openpyxl.}}
  \resumeSubHeadingListEnd


%--------TECHNICAL SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{AI/ML}{: LangChain, LangGraph, RAG Systems, Multi-Agent Architectures, Azure OpenAI, Groq LPU, Llama-3/4, Phi-3, Whisper, Cohere Embeddings, Prompt Engineering, Fine-Tuning, Open Source LLMS, VLLMs}
   }\vspace{-4pt}
   \item{
     \textbf{Vector Databases \& Search}{: pgvector (Azure PostgreSQL), ChromaDB, FAISS}
   }\vspace{-4pt}
   \item{
     \textbf{Backend}{: Python, FastAPI, PostgreSQL, SQLite, REST APIs, Async Programming, Nginx, Docker, Playwright}
   }\vspace{-4pt}
   \item{
     \textbf{Frontend}{: React, TypeScript, Tailwind CSS,  Streamlit}
   }\vspace{-4pt}
   \item{
     \textbf{Cloud \& DevOps}{: Azure (OpenAI, AD SSO, Key Vault, PostgreSQL, VM Scheduling, AI Foundry, Microsoft Foundry), Docker, APScheduler, GitLab, Git, SMTP Automation}
   }\vspace{-4pt}
   \item{
     \textbf{Security \& Observability}{: RBAC, Azure Key Vault, TLS, AES-256, SQL Injection Prevention, AI Agent Observability, AI Security}
   }
 \resumeSubHeadingListEnd


%--------AWARDS------------
\section{Awards \& Recognition}
 \resumeSubHeadingListStart
   \item{\small{\textbf{GreenRatna -- Performance of the Month Award} (December 2025), Adani Green Energy Limited: Recognized by AGEL leadership and stakeholders for designing and delivering impactful AI-driven portals and solutions. Work was appreciated by Hon'ble Chairman Shri Gautam Adani and received positive feedback across multiple teams at the organization.}}
 \resumeSubHeadingListEnd


%--------CERTIFICATIONS------------
\section{Certifications}
 \resumeSubHeadingListStart
   \item{\small{CCSK v4.1 Foundation Training -- Cloud Security $|$ Cloud Computing Fundamentals $|$ AICTE-Cisco Cyber Security Virtual Internship $|$ Google for Developers Cloud Bootcamp (GeeksforGeeks)}}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}